\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\lstset{basicstyle=\ttfamily\small, breaklines=true}

\title{QuBox v3 Architecture Refactoring\\[0.3em]\large Agent Handoff \& Status Document}
\author{Auto-generated during refactoring session}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\newpage

% ============================================================
\section{Project Goal}
% ============================================================

Refactor the \textbf{QuBox} cQED experiment-control library (at \texttt{E:\textbackslash qubox\_v2})
into a \textbf{clean, modular, extensible} architecture.
The library controls superconducting circuit-QED experiments on the
Quantum Machines OPX+ platform (SDK~1.2.x).

% ============================================================
\section{Three Codebases}
% ============================================================

\begin{tabular}{lp{10cm}}
\toprule
\textbf{Location} & \textbf{Role} \\
\midrule
\texttt{E:\textbackslash qubox\_v2} &
  Working copy --- this is what is being refactored in-place. \\
\texttt{C:\textbackslash Users\textbackslash jl82323\textbackslash Box\textbackslash Shyam Shankar
  Quantum Circuits Group\textbackslash Users\textbackslash Users\_JianJun\textbackslash
  JJL\_Experiments\textbackslash qubox} &
  Legacy monolithic qubox (for feature-parity reference). \\
\texttt{E:\textbackslash qubox\_v2\textbackslash API\_REFERENCE.md} &
  Existing v2 API reference (needs updating to v3). \\
\bottomrule
\end{tabular}

% ============================================================
\section{Approved Architecture (11 Layers)}
% ============================================================

\begin{lstlisting}
qubox_v2/
  core/             # L0  Config, errors, logging, protocols, types, utils
  calibration/      # L1  NEW - CalibrationStore (JSON-backed typed storage)
  hardware/         # L2  ConfigEngine, HardwareController, ProgramRunner, QueueManager
  devices/          # L3  DeviceManager (QCoDeS / InstrumentServer bridge)
  pulses/           # L4  PulseRegistry (simplified), IntegrationWeights, Waveforms
  programs/         # L5  QUA program factories (TO BE SPLIT from monolith)
    macros/         #     measureMacro, sequenceMacros (kept)
  experiments/      # L6  ExperimentBase + SessionManager + per-experiment classes
    spectroscopy/   #     ResonatorSpectroscopy, QubitSpectroscopy, ...
    time_domain/    #     TemporalRabi, PowerRabi, T1, T2Ramsey, T2Echo, ...
    calibration/    #     AllXY, DRAG, RB, ReadoutDiscrimination, ...
    cavity/         #     StorageSpectroscopy, FockResolved, ...
    tomography/     #     QubitStateTomo, FockTomo, WignerTomo
    spa/            #     SPAFluxOpt, SPAPumpFreqOpt
  analysis/         # L7  Fitting, plotting, discriminator, metrics
  simulation/       # L8  QuTiP cQED simulation
  gates/            # L9  Gate model + hardware abstraction
  compile/          # L10 Gate compilation / optimization
  optimization/     # L11 Parameter optimization
  tools/            #     Waveform generators, sweep builders
  gui/              #     Optional program GUI
  compat/           #     Backward-compatibility import shims
\end{lstlisting}

% ============================================================
\section{User-Approved Design Decisions}
% ============================================================

\begin{enumerate}
  \item \textbf{Overwrite} \texttt{E:\textbackslash qubox\_v2} in-place.
  \item \textbf{Break experiments} into individual classes
        (not keep monolith).
  \item \textbf{JSON files + Pydantic v2} for calibration persistence.
  \item \textbf{Target QM SDK 1.x only} (OPX+, not OPX1000).
  \item \textbf{Keep \texttt{manager.py}} (original PulseOperationManager)
        for backward compatibility alongside new \texttt{PulseRegistry}.
\end{enumerate}

% ============================================================
\section{Current Status --- What Is Done}
% ============================================================

\subsection{New files created (with real implementations, not stubs)}

\begin{longtable}{lrl}
\toprule
\textbf{File} & \textbf{Lines} & \textbf{Description} \\
\midrule
\endhead
\texttt{core/types.py}                       &  74 & Shared enums (ExecMode, DemodMode, PulseType, WaveformType) \\
\texttt{calibration/\_\_init\_\_.py}          &  24 & Package init \\
\texttt{calibration/models.py}               & 139 & Pydantic v2 models for calibration data \\
\texttt{calibration/store.py}                & 186 & CalibrationStore class (JSON persistence, snapshots) \\
\texttt{calibration/history.py}              &  54 & Timestamped calibration snapshots \\
\texttt{pulses/pulse\_registry.py}           & 491 & PulseRegistry facade (dual permanent/volatile store) \\
\texttt{pulses/integration\_weights.py}      & 195 & IntegrationWeightManager (extracted from POM) \\
\texttt{pulses/waveforms.py}                 & 221 & Waveform factory functions \\
\texttt{experiments/experiment\_base.py}     & 242 & New ExperimentBase ABC \\
\texttt{experiments/spectroscopy/resonator.py}  & 200 & ResonatorSpectroscopy, ResonatorPowerSpectroscopy \\
\texttt{experiments/spectroscopy/qubit.py}      & 139 & QubitSpectroscopy, QubitSpectroscopyEF \\
\texttt{experiments/time\_domain/rabi.py}       & 113 & TemporalRabi, PowerRabi \\
\texttt{experiments/time\_domain/coherence.py}  & 137 & T2Ramsey, T2Echo \\
\texttt{experiments/time\_domain/relaxation.py} &  40 & T1Relaxation \\
\texttt{experiments/time\_domain/chevron.py}    & 113 & RabiChevron, RamseyChevron \\
\texttt{experiments/calibration/readout.py}     & 382 & ReadoutDiscrimination, ReadoutButterfly, WeightsOpt \\
\texttt{experiments/calibration/gates.py}       & 181 & AllXY, DRAGCalibration, RandomizedBenchmarking \\
\texttt{experiments/calibration/reset.py}       &  96 & ActiveReset, LeakageBenchmarking \\
\texttt{experiments/cavity/storage.py}          & 230 & StorageSpectroscopy, NumSplitting, ChiRamsey \\
\texttt{experiments/cavity/fock.py}             & 154 & FockResolvedSpectroscopy, FockResolvedRamsey \\
\texttt{experiments/tomography/qubit\_tomo.py}  &  65 & QubitStateTomography \\
\texttt{experiments/tomography/fock\_tomo.py}   &  52 & FockStateTomography \\
\texttt{experiments/tomography/wigner\_tomo.py} &  91 & WignerTomography, SNAPOptimization \\
\texttt{experiments/spa/flux\_optimization.py}  & 246 & SPAFluxOptimization, SPAPumpFreqOptimization \\
\midrule
\multicolumn{3}{l}{\textbf{Session 4 additions}} \\
\midrule
\texttt{experiments/session.py}              & $\sim$200 & SessionManager (service container) \\
\texttt{experiments/result.py}               & $\sim$95  & AnalysisResult, FitResult dataclasses \\
\texttt{programs/spectroscopy.py}            &  31 & Re-export facade for spectroscopy programs \\
\texttt{programs/time\_domain.py}            &  34 & Re-export facade for time-domain programs \\
\texttt{programs/calibration.py}             &  28 & Re-export facade for calibration programs \\
\texttt{programs/readout.py}                 &  30 & Re-export facade for readout programs \\
\texttt{programs/cavity.py}                  &  34 & Re-export facade for cavity programs \\
\texttt{programs/tomography.py}              &  20 & Re-export facade for tomography programs \\
\texttt{MIGRATION.md}                        & $\sim$180 & v2$\rightarrow$v3 migration guide \\
\midrule
\multicolumn{3}{l}{\textbf{Sessions 10+ additions (analyze/plot, calibration, notebooks)}} \\
\midrule
\texttt{calibration/algorithms.py}           & $\sim$520 & Calibration algorithms: pulse-train, affine, chi, SPSA \\
\texttt{analysis/fitting.py}                 & (extended) & Added \texttt{fit\_and\_wrap()} bridge to FitResult \\
\texttt{experiments/experiment\_base.py}     & (extended) & Added \texttt{analyze()}/\texttt{plot()} protocol stubs \\
\texttt{hardware/program\_runner.py}         & (extended) & Fixed progress bar visibility \\
\texttt{experiments/spectroscopy/*.py}       & (extended) & analyze/plot for 8 spectroscopy classes \\
\texttt{experiments/time\_domain/*.py}       & (extended) & analyze/plot for 5 time-domain classes \\
\texttt{experiments/calibration/*.py}        & (extended) & analyze/plot for 13 calibration classes \\
\texttt{experiments/cavity/*.py}             & (extended) & analyze/plot for 10 cavity classes \\
\texttt{experiments/tomography/*.py}         & (extended) & analyze/plot for 4 tomography classes \\
\texttt{experiments/spa/*.py}                & (extended) & analyze/plot for 3 SPA classes \\
\texttt{calibration/models.py}               & (extended) & PulseTrainResult, FockSQRCalibration, MultiStateCalibration \\
\texttt{calibration/store.py}                & (extended) & Typed getters/setters for all calibration models \\
\texttt{notebooks/post\_cavity\_experiment.ipynb} & $\sim$72 cells & Full experiment notebook (v3 API) \\
\texttt{notebooks/post\_cavity\_calibrations.ipynb} & $\sim$27 cells & Calibration workflows notebook (v3 API) \\
\bottomrule
\end{longtable}

\subsection{Preserved files from v2 (unchanged)}

All of:
\texttt{core/} (config, errors, protocols, utils, logging),
\texttt{hardware/} (config\_engine, controller, program\_runner, queue\_manager),
\texttt{devices/} (device\_manager),
\texttt{pulses/manager.py}, \texttt{pulses/models.py},
\texttt{programs/cQED\_programs.py}, \texttt{programs/macros/} (measure, sequence),
\texttt{experiments/base.py} (ExperimentRunner), \texttt{experiments/legacy\_experiment.py},
\texttt{experiments/config\_builder.py}, \texttt{experiments/gates\_legacy.py},
\texttt{analysis/} (all files), \texttt{simulation/} (all), \texttt{gates/} (all),
\texttt{compile/} (all), \texttt{optimization/} (all), \texttt{tools/} (all),
\texttt{gui/} (all), \texttt{compat/} (all).

% ============================================================
\section{Current Status --- What Remains}
\label{sec:remaining}
% ============================================================

\textbf{All planned items are COMPLETE.}

\begin{enumerate}[label=\textbf{R\arabic*}]
  \item \label{R1} \textbf{\texttt{experiments/session.py}}
        --- \textcolor{green!60!black}{DONE}.
        \texttt{SessionManager} class created ($\sim$200 lines).
        Wires ConfigEngine + HardwareController + ProgramRunner +
        PulseRegistry + CalibrationStore + DeviceManager.

  \item \label{R2} \textbf{\texttt{experiments/result.py}}
        --- \textcolor{green!60!black}{DONE}.
        \texttt{AnalysisResult}, \texttt{FitResult} dataclasses created ($\sim$95 lines).
        Re-exports \texttt{RunResult} from \texttt{hardware.program\_runner}.

  \item \label{R3} \textbf{\texttt{programs/} split}
        --- \textcolor{green!60!black}{DONE}.
        Created 6 category re-export modules:
        \texttt{spectroscopy.py}, \texttt{time\_domain.py},
        \texttt{calibration.py}, \texttt{readout.py},
        \texttt{cavity.py}, \texttt{tomography.py}.
        Updated \texttt{programs/\_\_init\_\_.py} to import all 6.

  \item \label{R4} \textbf{\texttt{experiments/\_\_init\_\_.py}}
        --- \textcolor{green!60!black}{DONE} (was already comprehensive).

  \item \label{R5} \textbf{\texttt{pulses/\_\_init\_\_.py}}
        --- \textcolor{green!60!black}{DONE} (was already updated with PulseRegistry export).

  \item \label{R6} \textbf{\texttt{compat/\_\_init\_\_.py}}
        --- \textcolor{green!60!black}{DONE}.
        Added 30+ new redirect entries for v3 modules (calibration, program categories,
        experiment subdirectories, pulse registry, session, result, core types).

  \item \label{R7} \textbf{\texttt{API\_REFERENCE.md}}
        --- \textcolor{green!60!black}{DONE}.
        Updated to v3.0.0: added calibration layer (section 3.2),
        PulseRegistry/IntegrationWeightManager/waveforms docs,
        program category tables, SessionManager/ExperimentBase/AnalysisResult docs,
        experiment class hierarchy table, updated directory layout,
        updated migration guide with v3 SessionManager workflow,
        new quick-start example, updated design principles.
        \textbf{Sessions 10+:} Extended calibration section with typed CalibrationStore API,
        10 model reference table, 9-function algorithm table, analyze/plot protocol docs,
        per-experiment metrics reference table (20 experiments).

  \item \label{R8} \textbf{\texttt{MIGRATION.md}}
        --- \textcolor{green!60!black}{DONE}.
        Created comprehensive migration guide covering:
        what's new, what's preserved, import path changes,
        compat shim details, recommended migration path.

  \item \label{R9} \textbf{Optional: \texttt{Lab} facade class}
        --- NOT IMPLEMENTED (optional). Deferred for future work if needed.

  \item \label{R10} \textbf{Experiment analyze/plot protocol}
        --- \textcolor{green!60!black}{DONE}.
        All 43+ experiment classes now implement \texttt{analyze()} and \texttt{plot()}.
        \texttt{fit\_and\_wrap()} bridge in \texttt{analysis/fitting.py}.
        Typed \texttt{AnalysisResult}/\texttt{FitResult} containers.

  \item \label{R11} \textbf{Calibration infrastructure}
        --- \textcolor{green!60!black}{DONE}.
        Extended \texttt{CalibrationData} with PulseTrainResult, FockSQRCalibration,
        MultiStateCalibration models. Extended \texttt{CalibrationStore} with typed
        getters/setters for all 9 data categories. Created \texttt{calibration/algorithms.py}
        with 9 analysis functions.

  \item \label{R12} \textbf{Reference notebooks}
        --- \textcolor{green!60!black}{DONE}.
        \texttt{notebooks/post\_cavity\_experiment.ipynb}: 72-cell comprehensive experiment notebook.
        \texttt{notebooks/post\_cavity\_calibrations.ipynb}: 27-cell calibration workflow notebook.
        Both use unified \texttt{run() -> analyze() -> plot()} protocol.
\end{enumerate}

% ============================================================
\section{Key Design Patterns}
% ============================================================

\subsection{Experiment class pattern}
\begin{lstlisting}[language=Python]
class QubitSpectroscopy(ExperimentBase):
    def build_program(self, **params) -> qua.program: ...
    def run(self, **params) -> RunResult: ...
    def analyze(self, result, **kw) -> AnalysisResult: ...
    def plot(self, result, **kw): ...
\end{lstlisting}

\subsection{Unified three-step protocol}
All 43+ experiment classes follow:
\begin{lstlisting}[language=Python]
exp = ExperimentClass(session)
result = exp.run(...)                              # Execute on hardware
analysis = exp.analyze(result, update_calibration=True)  # Fit + metrics
exp.plot(analysis)                                 # Visualize
print(analysis.metrics)                            # Inspect results
\end{lstlisting}

\textbf{Key components:}
\begin{itemize}
  \item \texttt{analyze()} extracts data from \texttt{result.output}, fits physics models via
        \texttt{fit\_and\_wrap()}, returns \texttt{AnalysisResult} with \texttt{.fit}, \texttt{.fits},
        \texttt{.metrics}, \texttt{.data}
  \item If \texttt{update\_calibration=True}, persists results to \texttt{CalibrationStore}
  \item \texttt{plot()} accepts optional \texttt{ax} kwarg for multi-panel figures, returns \texttt{fig}
  \item \texttt{fit\_and\_wrap(x, y, model\_func, p0, model\_name)} inspects model function
        signature to extract parameter names $\rightarrow$ \texttt{FitResult.params} dict keys match
        model argument names exactly
\end{itemize}

\subsection{Calibration persistence pipeline}
\begin{lstlisting}[language=Python]
# Experiment -> analyze(update_calibration=True) -> CalibrationStore
#
# CalibrationStore data categories:
#   discrimination, readout_quality, frequencies, coherence,
#   pulse_calibrations, fit_history, pulse_train_results,
#   fock_sqr_calibrations, multi_state_calibration
#
# Calibration algorithms (calibration/algorithms.py):
#   fit_pulse_train, compute_corrected_knobs,
#   fit_multi_alpha_affine, apply_affine_correction,
#   fit_number_splitting, fit_chi_ramsey,
#   fit_fock_sqr, optimize_fock_sqr_iterative, optimize_fock_sqr_spsa
\end{lstlisting}

\subsection{SessionManager usage}
\begin{lstlisting}[language=Python]
with SessionManager("./cooldown_2025", qop_ip="10.0.0.1") as session:
    spec = QubitSpectroscopy(session)
    result = spec.run(pulse="x180", freq_start=6.13e9, ...)
    analysis = spec.analyze(result)
    spec.plot(analysis)
\end{lstlisting}

\subsection{Per-experiment metrics reference}

\begin{longtable}{llp{5cm}}
\toprule
\textbf{Experiment} & \textbf{Model} & \textbf{Key Metrics} \\
\midrule
\endhead
ResonatorSpectroscopy   & resonator\_spec\_model  & f0, kappa \\
QubitSpectroscopy       & qubit\_spec\_model      & f0, gamma \\
PowerRabi               & power\_rabi\_model      & g\_pi \\
TemporalRabi            & temporal\_rabi\_model   & f\_Rabi, T\_decay, pi\_length \\
T1Relaxation            & T1\_relaxation\_model   & T1 \\
T2Ramsey                & T2\_ramsey\_model       & T2, f\_det \\
T2Echo                  & T2\_echo\_model         & T2\_echo \\
AllXY                   & (ideal pattern)         & gate\_error \\
DRAGCalibration         & (zero-crossing)         & optimal\_alpha \\
RandomizedBenchmarking  & rb\_survival\_model     & p, avg\_gate\_fidelity, error\_per\_gate \\
IQBlob                  & two\_state\_discriminator & fidelity, angle, threshold \\
ReadoutButterfly        & butterfly\_metrics      & F, Q, V \\
StorageSpectroscopy     & resonator\_spec\_model  & f\_storage, kappa \\
StorageChiRamsey        & chi\_ramsey\_model      & chi, nbar, T2\_eff \\
FockResolvedT1          & T1 (per-Fock)           & T1\_fock\_0, T1\_fock\_1, \ldots \\
FockResolvedPowerRabi   & power\_rabi (per-Fock)  & g\_pi\_fock\_0, g\_pi\_fock\_1, \ldots \\
QubitStateTomography    & (Bloch vector)          & sx, sy, sz, purity \\
StorageWignerTomography & (parity $\rightarrow$ W)& W\_min, W\_max, negativity \\
SPAFluxOptimization     & (peak search)           & best\_dc, best\_freq \\
SPAPumpFreqOptimization & (argmax)                & best\_pump\_power, best\_pump\_detuning \\
\bottomrule
\end{longtable}

% ============================================================
\section{File Statistics}
% ============================================================

\begin{itemize}
  \item \textbf{107 Python files}, \textbf{34,988 total lines}
  \item Largest remaining monoliths:
    \begin{itemize}
      \item \texttt{legacy\_experiment.py}: 5,200 lines
      \item \texttt{cQED\_programs.py}: 2,898 lines
      \item \texttt{manager.py}: 2,362 lines
      \item \texttt{gates\_legacy.py}: 1,923 lines
      \item \texttt{macros/measure.py}: 1,575 lines
    \end{itemize}
\end{itemize}

% ============================================================
\section{Progress Log}
% ============================================================

\begin{description}
  \item[Session 1] Explored legacy qubox, v2 refactor, QM docs.
        Created approved architecture plan.
  \item[Session 2] Implemented core/types.py, calibration/ (models, store, history),
        pulses/ (pulse\_registry, integration\_weights, waveforms),
        experiment\_base.py, all 6 experiment subdirectories.
        Stopped mid-edit of pulses/\_\_init\_\_.py.
  \item[Session 3] Resumed. Created experiment subdirectory \texttt{\_\_init\_\_.py}
        files, experiment classes in all 6 categories.
        Stopped mid-edit of API\_REFERENCE.md.
  \item[Session 4] Resumed. Created HANDOFF.tex.
        Created \texttt{experiments/session.py} (SessionManager, $\sim$200 lines).
        Created \texttt{experiments/result.py} (AnalysisResult, FitResult, $\sim$95 lines).
        Split \texttt{programs/} into 6 category re-export modules.
        Updated \texttt{programs/\_\_init\_\_.py}.
        Updated \texttt{compat/\_\_init\_\_.py} with 30+ new v3 redirects.
        Updated \texttt{API\_REFERENCE.md} to v3.0.0 (calibration, pulses, experiments, programs).
        Created \texttt{MIGRATION.md} (comprehensive v2$\rightarrow$v3 guide).
        Updated this HANDOFF.tex with final status.
        \textbf{All R1--R8 items COMPLETE. R9 (Lab facade) deferred as optional.}

  \item[Sessions 5--9] \textbf{API Consistency \& Modernization.}
        Created \texttt{hardware/qua\_program\_manager.py} compatibility facade.
        Notebook generation (\texttt{notebooks/qubox\_v2\_usage.ipynb}).
        Migrated \texttt{seq\_1\_device/} data and validated end-to-end flow.
        Comprehensive codebase-wide fixes detailed in Section~\ref{sec:api-modernization}.

  \item[Sessions 10+] \textbf{Experiment analyze/plot \& Calibration Infrastructure.}
        Implemented full \texttt{analyze()}/\texttt{plot()} protocol across all 43+ experiment classes.
        Created \texttt{fit\_and\_wrap()} bridge in \texttt{analysis/fitting.py}.
        Fixed progress bar visibility in \texttt{hardware/program\_runner.py}.
        Extended \texttt{calibration/models.py} with PulseTrainResult, FockSQRCalibration,
        MultiStateCalibration.
        Extended \texttt{calibration/store.py} with typed getters/setters for 9 data categories.
        Created \texttt{calibration/algorithms.py} ($\sim$520 lines, 9 analysis functions).
        Updated \texttt{calibration/\_\_init\_\_.py} exports.
        Created \texttt{notebooks/post\_cavity\_experiment.ipynb} (72 cells, full experiment reference).
        Created \texttt{notebooks/post\_cavity\_calibrations.ipynb} (27 cells, calibration workflows).
        Updated \texttt{API\_REFERENCE.md} with protocol docs, model tables, algorithm reference.
        Updated \texttt{HANDOFF.tex} with final status.
        \textbf{All R1--R12 items COMPLETE (R9 deferred as optional).}

  \item[Sessions 12+] \textbf{Plot equation display, unit fixes, documentation.}
        Added \texttt{build\_fit\_legend()} function to \texttt{analysis/fitting.py} --- generates
        multi-line legend string with model equation and fitted parameter values for
        consistent figure annotations.
        Added \texttt{.equation} attribute to all physics models in \texttt{cQED\_models.py};
        stored in \texttt{FitResult.metadata["equation"]} by \texttt{fit\_and\_wrap()}.
        Updated all \texttt{plot()} methods across 9 experiment files (20+ methods) to use
        \texttt{build\_fit\_legend()} with outside-plot legend placement
        (\texttt{bbox\_to\_anchor=(1.05, 1)}).
        Fixed auto\_p0 unit mismatch bugs:
        \texttt{T2Ramsey.analyze()}: \texttt{f\_det\_guess = qb\_detune / 1e9} (Hz $\rightarrow$ GHz = 1/ns);
        \texttt{StorageChiRamsey.analyze()}: FFT-based chi estimate replacing arbitrary \texttt{1e6}.
        Added \texttt{analyze()}/\texttt{plot()} to \texttt{ReadoutWeightsOptimization}.
        Updated \texttt{post\_cavity\_experiment.ipynb} with explicit p0 values converted
        from legacy $\mu$s/MHz convention to ns/GHz convention.
        Updated \texttt{API\_REFERENCE.md} with \texttt{build\_fit\_legend()}, \texttt{FitResult.metadata},
        unit convention table, corrected experiment class hierarchy (48 classes total).
        Updated this \texttt{HANDOFF.tex}.
\end{description}

% ============================================================
\section{API Consistency \& Modernization (Sessions 5--9)}
\label{sec:api-modernization}
% ============================================================

A comprehensive sweep of the codebase was performed to eliminate all stale
imports, broken constructor calls, naming inconsistencies, and documentation
inaccuracies.  All changes below have been verified with import tests.

\subsection{Phase 1: SessionManager Runtime Fixes}

\texttt{experiments/session.py} had \textbf{6 broken call sites} that would
crash at runtime.  Each was corrected to match the actual v3 constructor
signatures:

\begin{longtable}{p{5cm}p{4cm}p{5cm}}
\toprule
\textbf{Call Site} & \textbf{Bug} & \textbf{Fix} \\
\midrule
\endhead
\texttt{ConfigEngine()} &
  \texttt{hardware\_json=}, \texttt{pulse\_json=} (no such params) &
  \texttt{hardware\_path=} (single path) \\
\texttt{QueueManager()} &
  \texttt{controller=self.hardware} &
  \texttt{runner=self.runner} \\
\texttt{PulseOperationManager()} &
  \texttt{POM(self.config\_engine)} &
  \texttt{POM.from\_json(path)} or \texttt{POM()} \\
\texttt{PulseRegistry()} &
  \texttt{PulseRegistry(self.config\_engine)} &
  \texttt{PulseRegistry()} (no args) \\
\texttt{DeviceManager()} &
  \texttt{autoload=} (no such param) &
  \texttt{DeviceManager(path)} + manual \texttt{instantiate\_all()} \\
\texttt{burn\_pulses()} &
  \texttt{self.pulse\_mgr.burn()} (no such method) &
  \texttt{config\_engine.merge\_pulses(pom)} \\
\bottomrule
\end{longtable}

\subsection{Phase 2: Broken Imports in gates/hardware/}

Four files imported from \texttt{qubox\_v2.pulse\_manager}, which does not exist:

\begin{longtable}{lp{9cm}}
\toprule
\textbf{File} & \textbf{Fix} \\
\midrule
\endhead
\texttt{gates/hardware/displacement.py} &
  \texttt{from qubox\_v2.analysis.pulseOp import PulseOp};
  \texttt{from qubox\_v2.core.types import MAX\_AMPLITUDE} \\
\texttt{gates/hardware/qubit\_rotation.py} & Same as displacement \\
\texttt{gates/hardware/snap.py} &
  \texttt{from qubox\_v2.analysis.pulseOp import PulseOp} \\
\texttt{gates/hardware/sqr.py} & Same as snap \\
\bottomrule
\end{longtable}

\subsection{Phase 3: Package Name in File Headers}

$\sim$33 files in \texttt{gates/} and \texttt{compile/} had incorrect header
comments (\texttt{\# qubox/gates\_v2/...} or \texttt{\# qubox/...}).
All updated to \texttt{\# qubox\_v2/...}.
Additionally, error messages in \texttt{compile/gpu\_accelerators.py} referenced
\texttt{"qubox.compile.evaluators"} --- corrected to
\texttt{"qubox\_v2.compile.evaluators"}.

\subsection{Phase 4: API\_REFERENCE.md Corrections}

Updated all inaccurate constructor signatures and example snippets:

\begin{itemize}
  \item \texttt{ConfigEngine}: \texttt{hardware\_json=} $\rightarrow$ \texttt{hardware\_path=}; removed \texttt{pulse\_json=}
  \item \texttt{HardwareController}: added \texttt{qmm} parameter, removed \texttt{qop\_ip}
  \item \texttt{ProgramRunner}: corrected to 3 params (\texttt{qmm}, \texttt{controller}, \texttt{config\_engine})
  \item \texttt{ExecMode}: \texttt{RUN} $\rightarrow$ \texttt{HARDWARE}
  \item \texttt{QueueManager}: \texttt{controller=} $\rightarrow$ \texttt{runner=}
  \item \texttt{DeviceManager}: removed \texttt{autoload=}, \texttt{close\_all()}
  \item \texttt{PulseOperationManager}: corrected constructor
  \item \texttt{PulseRegistry}: corrected constructor (no args)
  \item Quick-Start examples C and D: corrected hardware layer + queue examples
\end{itemize}

\subsection{Phase 5: Explicit \texttt{\_\_all\_\_} for Wildcard-Import Inits}

Added explicit \texttt{\_\_all\_\_} declarations to prevent namespace pollution:

\begin{itemize}
  \item \texttt{tools/\_\_init\_\_.py} --- 2 generators + 10 waveform functions
  \item \texttt{optimization/\_\_init\_\_.py} --- 6 optimization routines
  \item \texttt{simulation/\_\_init\_\_.py} --- 8 exports (circuitQED, Term,
        solve\_lindblad, DriveGenerator, etc.)
\end{itemize}

\subsection{Phase 6: External LO Detection Fix}

\texttt{hardware/controller.py} methods \texttt{\_element\_octave\_rf\_out()}
and \texttt{\_is\_external\_lo()} were using \texttt{self.qm.get\_config()}
which returns the SDK-normalized config where \texttt{RF\_inputs} is stripped.
This caused \texttt{UnableToSetFrequencyError} for elements connected to
external LO sources.

\textbf{Fix:} Both methods now use \texttt{self.config.hardware\_base} (the
original un-normalized config) to correctly detect external LO routing.

\subsection{Phase 7: Stale Import in tools/generators.py}

Two broken imports in \texttt{tools/generators.py}:
\begin{itemize}
  \item \texttt{from ..pulse\_manager import PulseOperationManager}
        $\rightarrow$ \texttt{from ..pulses.manager import PulseOperationManager}
  \item \texttt{from ..gates\_legacy import QubitRotation}
        $\rightarrow$ \texttt{from ..experiments.gates\_legacy import QubitRotation}
\end{itemize}

\subsection{Verification}

All changes verified with comprehensive import tests:
\begin{lstlisting}
python -c "
from qubox_v2.tools.generators import register_rotations_from_ref_iq
from qubox_v2.gates.hardware.displacement import DisplacementHardware
from qubox_v2.gates.hardware.qubit_rotation import QubitRotationHardware
from qubox_v2.gates.hardware.snap import SNAPHardware
from qubox_v2.gates.hardware.sqr import SQRHardware
from qubox_v2.experiments.session import SessionManager
from qubox_v2.experiments.legacy_experiment import cQED_Experiment
from qubox_v2.compile.api import compile_with_ansatz
from qubox_v2.hardware.controller import HardwareController
from qubox_v2.hardware.qua_program_manager import QuaProgramManager
from qubox_v2.optimization import scipy_minimize, cma_es, spsa
from qubox_v2.tools import drag_gaussian_pulse_waveforms
print('All imports passed successfully')
"
\end{lstlisting}

Additionally, a codebase-wide grep confirmed \textbf{zero remaining stale
references} to \texttt{qubox\_v2.pulse\_manager}, \texttt{..gates\_legacy}
(without \texttt{experiments} prefix), or bare \texttt{qubox.} package names
(outside of the intentional \texttt{compat/} module).

\subsection{Files Modified (Modernization Summary)}

\begin{longtable}{lrl}
\toprule
\textbf{Category} & \textbf{Count} & \textbf{Files} \\
\midrule
\endhead
Critical runtime fix     & 1  & \texttt{experiments/session.py} \\
Broken imports           & 4  & \texttt{gates/hardware/\{displacement,qubit\_rotation,snap,sqr\}.py} \\
File headers             & 33 & \texttt{gates/**/*.py}, \texttt{compile/**/*.py} \\
Error messages           & 1  & \texttt{compile/gpu\_accelerators.py} \\
API documentation        & 1  & \texttt{API\_REFERENCE.md} \\
Init exports             & 3  & \texttt{tools/}, \texttt{optimization/}, \texttt{simulation/} \texttt{\_\_init\_\_.py} \\
External LO fix          & 1  & \texttt{hardware/controller.py} \\
Stale imports            & 1  & \texttt{tools/generators.py} \\
Compat facade            & 1  & \texttt{hardware/qua\_program\_manager.py} (created) \\
\midrule
\textbf{Total}           & \textbf{$\sim$46} & \\
\bottomrule
\end{longtable}

\end{document}
